Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-04-18 Documents/M1/realizableFermionicM1/sections/appendix.tex
Removed CFL from PC2, RKCB2 and SSP2332.
Working on text discussing IMEX schemes.
Added 'IMEX PARSD'.

\section{Butcher Tableau for IMEX Schemes}

@@

Another positivity-preserving IMEX scheme was given in \cite{mcclareen_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclareen_2008}).  
This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 0.5, \nonumber \\
  a_{33} &= 1.0. \nonumber
\end{align}
And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.
A common choice of this scheme is $c_{sch} = 0.3$.

@@

We compare the performance of the positivity-preserving IMEX schemes with two other, non-positive, schemes.  
The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015}.  
We refer to this scheme as IMEX RKCB2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 2/5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 2/5, \nonumber \\
  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
CFL ...

@@

The second scheme we use for comparison is the second-order accurate IMEX scheme given in \cite{pareschiRusso_2005}.  
We refer to this scheme as IMEX SSP2332.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 1/2, \nonumber \\
  \tilde{a}_{31} &= 1/2, \quad \tilde{a}_{32} = 1/2, \nonumber \\
  a_{11} &= 1/4, \nonumber \\
  a_{22} &= 1/4, \nonumber \\
  a_{31} &= 1/3, \quad a_{32} = 1/3, \quad a_{33} = 1/3. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
CFL ...

>>>>

\section{Butcher Tableau for IMEX Schemes}
\label{app:butcherTables}

@@

Another positivity-preserving IMEX scheme was given in \cite{mcclareen_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclareen_2008}).  
This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 0.5, \nonumber \\
  a_{33} &= 1.0. \nonumber
\end{align}
And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.

\paragraph{IMEX PARSD}

We have found a second-order accurate in the streaming limit, diffusion accurate, positivity-preserving IMEX scheme of type $ARS$, which we refer to as IMEX PARSD.  
This scheme allows for has a $c_{sch}= 1 - 2\epsilon$ which can arbitrary close to 1 by setting $\epsilon$ a arbitrary small positive value.
Here we give an example by setting $\epsilon=0.1$.
\begin{align}
  \tilde{a}_{21} & = 1.0, \nonumber \\
  \tilde{a}_{31} & = 0.5, \quad \tilde{a}_{32} = 0.5, \nonumber \\
  a_{22} & = 1.0, \nonumber \\
  a_{32} & = 0.4 \,( = 0.5 - \epsilon\,), \quad a_{33} = 0.6 \,( = 0.5 + \epsilon\,). \nonumber
\end{align} 
This scheme is also GSA and needs only two compute for implicit terms each time-step.

@@

We compare the performance of the positivity-preserving IMEX schemes with two other, non-positive, schemes.  
The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015}.  
We refer to this scheme as IMEX RKCB2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 2/5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 2/5, \nonumber \\
  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.

@@

The second scheme we use for comparison is the second-order accurate IMEX scheme given in \cite{pareschiRusso_2005}.  
We refer to this scheme as IMEX SSP2332.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 1/2, \nonumber \\
  \tilde{a}_{31} &= 1/2, \quad \tilde{a}_{32} = 1/2, \nonumber \\
  a_{11} &= 1/4, \nonumber \\
  a_{22} &= 1/4, \nonumber \\
  a_{31} &= 1/3, \quad a_{32} = 1/3, \quad a_{33} = 1/3. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
